Pteropod biomarker analysis

### 2018-03-02 index.Rmd
eval.Rmd changed to index.Rmd
renderPrint and ggplot for rmarkdown shiny

      # coeff summary
      out <- x %>% 
        summary %>% 
        .$coefficients %>% 
        .[-1, c(1, 4)] %>% 
        data.frame %>% 
        rownames_to_column('env_lab') %>% 
        mutate(
          bio_lab = yvar,
          Est = round(Estimate, 2), 
          Pvl = p_ast(Pr...t..)
        ) %>% 
        select(bio_lab, env_lab, Est, Pvl)

@@

@@

## LPX

```{r}
knitr::kable(filter(mods, bio_lab %in% 'LPX'), caption = 'LPX')
```

>>>>

      # rsq
      rsq <- summary(x) %>% 
        .$r.squared

      # coeff summary
      out <- x %>% 
        summary %>% 
        .$coefficients %>% 
        .[-1, c(1, 4)] %>% 
        data.frame %>% 
        rownames_to_column('env_lab') %>% 
        mutate(
          bio_lab = yvar,
          Rsq = round(rsq, 2),
          Est = round(Estimate, 2), 
          Pvl = p_ast(Pr...t..)
        ) %>% 
        select(bio_lab, env_lab, Rsq, Est, Pvl)

@@

renderPrint({summary(md())})

renderPlot({
  toplo <- md()$model %>% 
    gather('var', 'val', -1)

  ggplot(toplo, aes_string(x='val', y=names(toplo)[1])) +
    geom_point() + 
    facet_wrap(~var, ncol = 2, scales = 'free_x') + 
    theme_bw(base_family = 'serif') + 
    geom_smooth(method = 'lm') + 
    theme(axis.title.x = element_blank())

}, height = 300, width = 600)

@@

## LPX
```{r}
knitr::kable(filter(mods, bio_lab %in% 'LPX'), caption = 'LPX')
```
